---
title: "nflcombineR"
author: "Jacob Lexner"
date: "2025-12-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## My R Package

For my R package I used an NFL combine dataset and created functions and plots to analyze players and to view players combine stats.Shown below are some of the functions in the packages.

```{r}
library(nflcombineR)
compare_players("Josh Allen", "Tom Brady")
player_summary("Kenny Jackson")
position_summary("C")
```

## S3 Object

Shown below, I created a function that builds an S3 object by taking the players name, position and college in a list and assigning it to the class "player".
```{r}
p<-player("Josh Allen","QB", "Wyoming")
class(p)
```

## Plots for the Package

Below I show 2 plots I made for my package to show the average 40 times and bench reps for players by positions.

```{r, warning=FALSE}
plot_forty()
plot_bench()
```

With this package you can find more information about NFL players combine history as well see averages of positions in the combine and even compare players combine stats against one another. It is built in that if you put a player in that is not in the data that it will inform you that the player is not in the data and the function will not run through. I chose MIT LICENSE because it allows use of my package in broad use. 

